Constant-round Blind Classical Verification of Quantum Sampling

### 2020-08-02 preliminaries.tex
Add QPIP streaming model discussion in preliminary

We model the interaction between a (almost classical) client and a quantum server following \cite{FOCS:Mahadev18a}.

\Ethan{``Streaming" model; can send qubits one-by-one to let client measure many qubits this way.

Tone: Review/introduce. It's not new. Use Urmila's use case as example.}

>>>>

We model the interaction between a (almost classical) client and a quantum server following \cite{FOCS:Mahadev18a}.
When the client has limited quantum capabilities, this is a ``streaming" model.
That is, the server can send qubits one-by-one to let client measure them sequentially.
even if the client cannot hold the entire quantum message,
We do not care about rounds-complexity unless the client is fully classical,
in which case this model specializes to the standard rounds-based model.
